Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Fixes to-do (expands on I, P, and B frame example)

The combination of deadlines and partial reliability leads to \emph{dependency
management} as an important transport service.
% There is no point in sending data that cannot be used because it depends on
% previous data that was not received.
In particular, data should never be sent when it relies on a previous
transmission that was never received. Providing this service is complicated by
the two ways in which data can be \emph{useful} to applications: it may itself
be played out, or it may be needed as part of the application's decoding chain.
For example, I frames provide utility both in being played out, and as
foundations for subsequent P and B frames. As a result, dependencies may take
higher priority than deadlines.
\todo{Review A: Some video-specific jargon (I, P, B frames) could be
expanded/explained.}
% : data may be sent even if it
% cannot be played out, if it is necessary for the decoding of other data.

>>>>

The combination of deadlines and partial reliability leads to \emph{dependency
management} as an important transport service.
% There is no point in sending data that cannot be used because it depends on
% previous data that was not received.
In particular, data should never be sent when it relies on a previous
transmission that was never received. Providing this service is complicated by
the two ways in which data can be \emph{useful} to applications: it may itself
be played out, or it may be needed as part of the application's decoding chain.
Interdependencies between frames of video exist within a number of codecs,
including MPEG-1 \cite{le1991mpeg}, and newer codecs such as H.264
\cite{wiegand2003overview}. As an example, we consider MPEG-1 video:
I-frames are independent, while P- and B-frames contain only the changes 
since the previous frame (P) or between frames (B), and so are dependent on
the successful arrival of other frames. An I-frame may not arrive in time
to be played out, but may need to be sent to ensure that dependent P- and
B-frames are useful.
